Real-Time Activity Classification by Match Filtering using Body-Worn Accelerometers

### 2016-06-23 notes/paper/paper.tex
Added Bryan's portion (raw). Still need to parse through it to fit it into the paper.

We chose this method for its simplicity and robustness against outliers in our training set. We anticipate that the user will have idle motion at the start and end of their training duration when they activate the training mode and with possible disruptions during the process.
%
\section{Performance and Throughput}
%
The Kinetisense sensor was used for the performance analysis in this paper.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user for the purpose of analyzing the performance.
A separate instance of walking data has been used specifically for training the classifier.
In figure \ref{fig:MF_performance}, \subref{fig:frac_walking_jogging} and \subref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
As we would expect, walking data matches better to walking data than the other activities.
ROC curves were produced from these corresponding results in \subref{fig:roc_walking_jogging} and \subref{fig:roc_walking_bicycling} to illistrate the effectiveness of the matched-filter as a classifier.
Figure \ref{fig:MF_performance} shows the comparison to bicycling.
Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from bicycling.
%
%\begin{figure}[!tbp]
%\RawFloats
%  \centering
%     \begin{minipage}[b]{0.45\textwidth}
%        \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_run.png}
%        \caption{\label{ROC_walk_to_run_fig}ROC curve with a downsample factor of 8}
%     \end{minipage}
%     \hfill
%     \begin{minipage}[b]{0.45\textwidth}
%     \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_bike.png}
%        \caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
%     \end{minipage}
%\caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
%\end{figure}
%
\begin{figure}[!ht]
  %\captionsetup[subfigure]{labelformat=empty}
  \centering
  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
  \quad
  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
  \centering
  \quad
  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_run.png}}
  \centering
  \quad
  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced with decimation 8}
  \label{fig:MF_performance}
\end{figure}
%
%\FloatBarrier
reference to figure \ref{fig:MF_performance}
%
\begin{figure}[!ht]
   \centering
   \includegraphics[width=1.0\textwidth]{one_and_two_references.png} \label{fig:timing_refs}
   \caption{Timing results with varying sampling frequencies on the MSP432 micro-controller processor comparing the timing between using one vs two references for classification with the matched-filter. The time window used for activity classification is 4.0 seconds}
\end{figure}
%
\section{Conclusion}
conclusion text.
%
\appendices
%
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi
%
\bibliographystyle{plain}
\bibliography{reference}
\end{document}

>>>>

We chose this method for its simplicity and robustness against outliers in our training set. We anticipate that the user will have idle motion at the start and end of their training duration when they activate the training mode and with possible disruptions during the process.
%
\section{Performance and Throughput}
%
The Kinetisense sensor was used for the performance analysis in this paper.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user for the purpose of analyzing the performance.
A separate instance of walking data has been used specifically for training the classifier.
In figure \ref{fig:MF_performance}, \subref{fig:frac_walking_jogging} and \subref{fig:frac_walking_bicycling} show the fraction of the correlation results that exceed the given correlation threshold when comparing the walking data reference to the given activity.
As we would expect, walking data matches better to walking data than the other activities.
ROC curves were produced from these corresponding results in \subref{fig:roc_walking_jogging} and \subref{fig:roc_walking_bicycling} to illistrate the effectiveness of the matched-filter as a classifier.
Figure \ref{fig:MF_performance} shows the comparison to bicycling.
Because the bicycling motions are considerably different from walking relative to jogging, we would expect better performance from bicycling.
%
%\begin{figure}[!tbp]
%\RawFloats
%  \centering
%     \begin{minipage}[b]{0.45\textwidth}
%        \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_run.png}
%        \caption{\label{ROC_walk_to_run_fig}ROC curve with a downsample factor of 8}
%     \end{minipage}
%     \hfill
%     \begin{minipage}[b]{0.45\textwidth}
%     \includegraphics[angle=0,width=\textwidth]{ROC_walk_to_bike.png}
%        \caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
%     \end{minipage}
%\caption{\label{ROC_walk_to_bike_fig}ROC curve with a downsample factor of 8}
%\end{figure}
%
\begin{figure}[!ht]
  %\captionsetup[subfigure]{labelformat=empty}
  \centering
  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
  \quad
  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
  \centering
  \quad
  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_run.png}}
  \centering
  \quad
  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=.45\textwidth]{ROC_walk_to_bike.png}}
  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced with decimation 8}
  \label{fig:MF_performance}
\end{figure}
%
%\FloatBarrier
reference to figure \ref{fig:MF_performance}
%
\begin{figure}[!ht]
   \centering
   \includegraphics[width=1.0\textwidth]{one_and_two_references.png} \label{fig:timing_refs}
   \caption{Timing results with varying sampling frequencies on the MSP432 micro-controller processor comparing the timing between using one vs two references for classification with the matched-filter. The time window used for activity classification is 4.0 seconds}
\end{figure}
%
MSP432 role
The Texas Instrument - MSP432P401R is a low power plus performance microcontroller that is based on the ARM 32-Bit Cortex-M4F processor and is used to run the real-time activity classification algorithm.
Some of the notable features of the MSP432P410R is having a clock frequency of 48 MHz, 64 kB SRAM, 256 kB Flash Memory, and has an IEEE 754 – compliant single – precision Floating – Point Unit (FPU).
The FPU is important for running the real-time activity classification algorithm because it gives us the ability to represent small and large numbers.
The alternative to an FPU would be a fixed-point, the problem with fixed-point is the dilemma between precision and range.
For this application you need to have both and the FPU gives us that.
The 64 kB of SRAM allows the microcontroller to have sufficient space to process the data acquired when executing the real-time activity classification algorithm.
The 256 kB is more than enough of flash memory to store the program.
Lastly, the clock frequency of 48 MHz allows the microcontroller to have a high performance by allowing a high number of instruction cycles that ultimately allows for faster code execution.
%
Execution speed process
When testing the execution speed of the real-time activity classification algorithm on the MSP432P401R, one of the General-Purpose Input/Output (GPIO) pin was used that was connected to a simple (Light-emitted diode) LED.
To turn on the LED that was connected to the GPIO, a 3.3 Volt is required to light up the LED.
Therefore, before entering the algorithm that handles the real-time activity classification, the GPIO pin is initially set HIGH to 3.3 Volts which lights up the LED.
When the real-time activity classification algorithm is finished, the GPIO is set LOW to 0 Volts immediately setting the LED off. The execution time is then recorded by using an oscilloscope to determine how long the GPIO was set HIGH to 3.3 Volts.
The oscilloscope used was “Analog Discovery 100MSPS USB Oscilloscope and Logic Analyzer”.
[I can show an example of this process, but i do not know of what data.
In other words acquired the execution speed of what? If you plan on you using this piece let me know so I can get an image of the oscilliscope displaying the execution speed.]
\section{Conclusion}
conclusion text.
%
\appendices
%
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi
%
\bibliographystyle{plain}
\bibliography{reference}
\end{document}
